How resource abundance and stochasticity affect animals’ spatial needs

### 2023-05-19 writing/conference-abstracts/2023-grs-abstract.Rmd
added more data contributors

---
title: "How resource abundance and stochasticity affect animals’ spatial needs"
date: "`r Sys.Date()`"
author:
  - name: Stefano Mezzini
    email: stefano.mezzini@ubc.ca
    institute: ubco
  - name: Emília Patrícia Medici
    institute: [tapir, iucn, escas]
  - name: Michael J. Noonan
    email: michael.noonan@ubc.ca
    institute: ubco
institute:
  - ubco: The Irving K. Barber Faculty of Science, The University of British Columbia, Okanagan Campus, Kelowna, Canada.
  - tapir: Lowland Tapir Conservation Initiative (LTCI), Instituto de Pesquisas Ecológicas (IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - iucn: IUCN SSC Tapir Specialist Group (TSG), Campo Grande, Brazil.
  - escas: Escola Superior de Conservação Ambiental E Sustentabilidade (ESCAS/IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
output:
  bookdown::pdf_document2:
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
    toc: false
    number_sections: false
---

>>>>

---
title: "How resource abundance and stochasticity affect animals’ spatial needs"
date: "`r Sys.Date()`"
author:
  - name: Stefano Mezzini
    email: stefano.mezzini@ubc.ca
    institute: ubco
  - name: Adam T. Ford
    institute: ubco
  - name: Jacob R. Goheen
    institute: wyom
  - name: E. Patrícia Medici
    institute: [tapir, iucn, escas]
  - name: Michael J. Noonan
    email: michael.noonan@ubc.ca
    institute: ubco
institute:
  - ubco: The Irving K. Barber Faculty of Science, The University of British Columbia, Okanagan Campus, Kelowna, Canada.
  - wyom: Department of Zoology and Physiology, University of Wyoming, Laramie, Wyoming, United States of America
  - tapir: Lowland Tapir Conservation Initiative (LTCI), Instituto de Pesquisas Ecológicas (IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
  - iucn: IUCN SSC Tapir Specialist Group (TSG), Campo Grande, Brazil.
  - escas: Escola Superior de Conservação Ambiental E Sustentabilidade (ESCAS/IPÊ), Rodovia Dom Pedro I, km 47, Nazaré Paulista, São Paulo 12960-000, Brazil.
output:
  bookdown::pdf_document2:
    pandoc_args:
      - '--lua-filter=../scholarly-metadata.lua'
      - '--lua-filter=../author-info-blocks.lua'
    toc: false
    number_sections: false
---
